\section*{Experience}

\begin{cventries}
	\cventry{Research Intern}
	{Oracle Labs Z{\"u}rich}
	{August 2020 --- February 2021} % Date(s)
	{}
	{%
		\begin{cvitems}
		\item Working on a special mode for the \cvlanguage{GraalVM} Java Bytecode compiler, itself written in \cvlanguage{Java}, focusing on fast compilation times.
		\item Testing and benchmarking impact on compilation time as well as program runtime.
		\end{cvitems}
	}
	\cventry{Teaching Assistant, \emph{Object-Oriented Programming}}
	{EPFL --- École Polytechnique Fédérale de Lausanne}
	{February 2021 --- July 2021} % Date(s)
	{}
	{%
		\begin{cvitems}
		\item Mentored groups of students, giving advice on their semester-long project written in \cvlanguage{C++}.
		\item Helped rewrite and modernize the course's tutorial on GUI development with \cvlanguage{Qt} and \cvlanguage{OpenGL}.
		\item Graded exams and assignments.
		\end{cvitems}
	}
\cventry{Teaching Assistant, \emph{Various courses}}
	{University of Groningen}
	{September 2018 --- July 2020} % Date(s)
	{}
	{%
		\begin{cvitems}
		\item Taught students in support lectures and exercise sessions for various courses in the program.
		\item Provided students with guidance and feedback on programming (\cvlanguage{Java}, \cvlanguage{C}, \cvlanguage{Haskell}) and theory\\ (Program Correctness, Theory of Computation) assignments.
		\item Graded exams and assignments.
		\end{cvitems}
	}
	\cventry{Software Developer} % Organization
	{University of Groningen}
	{October 2019 --- January 2020} % Date(s)
	{}
	{
		\begin{cvitems}
		\item Implemented an automated grading system for Computer Graphics programming assignments, which was used by 100+ students in the Spring 2020 edition of the course.
		\item Devised an algorithm to compare student submissions to a reference solution, implemented in \cvlanguage{C++}.
		\item Integrated the system with the University's code submission platform, built with a \cvlanguage{Node.js} server running submitted programs on \cvlanguage{LXC} containers.
		\item Wrote unit and integration tests.
		\end{cvitems}
	}
	%\cventry{Requirements Engineering Group Project} % Organization
	%{Product Owner}
	%{October 2019 --- January 2020} % Date(s)
	%{}
	%{%
	%	\begin{cvitems}
	%	\item Pitched and subsequently led a team of 4 students in developing a web app to share and rate code snippets for learning purposes, building a \cvlanguage{Python} backend with \cvlanguage{Flask} and a \cvlanguage{JavaScript} frontend with \cvlanguage{Vue}.
	%	\item Personally conducted customer interviews and elicited application requirements.
	%	\item Deployed project on \cvlanguage{AWS} using \cvlanguage{Docker} containers, storing data in a \cvlanguage{PostgreSQL} database.
	%	\end{cvitems}
	%}
	%\cventry{Software Engineering Group Project} % Organization
	%{Scrum Master}
	%{January 2019 --- June 2019} % Date(s)
	%{}
	%{%
	%	\begin{cvitems}
	%	\item Led a team of 10 students in developing a desktop-based visualizer and editor of volumetric data in an Agile environment, using \cvlanguage{C++} with \cvlanguage{Qt} and \cvlanguage{OpenGL}.
	%	\item Planned sprint meetings, evaluated user stories, continuously assessed code and documentation quality, and implemented filtering logic for data editing.
	%	\end{cvitems}
	%}
\end{cventries}
