% \cvsection{Research Interests}
% \vspace{1em}
% \begin{cvitems}
% 	\item Programming Language Research
% 	\item Computer Graphics
% 	\item Software Engineering
% \end{cvitems}
% \vspace{1em}


\cvsection{Projects}
\begin{cventries}
    \cventry
    {Bachelor's Project} % Empty position
    {Locally refinable Gradient Meshes} % Project
    {} % Empty location
    {} % Empty date
    {
        An interactive visualizer of 3D volumetric data, implementing data filtering based on the Connected Components Max Tree algorithm.\newline
		It supports various filtering attributes such as volume, surface area, or elongation.
    }\\\vspace{1em}
    \cventry
    {Course Related} % Empty position
    {FLIS - Filtering Visualizer} % Project
    {} % Empty location
    {} % Empty date
    {
        An interactive visualizer of 3D volumetric data, implementing data filtering based on the Connected Components Max Tree algorithm.\newline
		It supports various filtering attributes such as volume, surface area, or elongation.
    }\\\vspace{1em}
    \cventry
    {Course Related} % Empty position
    {\href{https://github.com/CRefice/isolation}{Isolation\hspace{0.15cm}\faGithubSquare}} % Project
    {} % Empty location
    {} % Empty date
    {
        My winning entry for the OpenGL competition organized by the Computer Graphics course at the University of Groningen.\newline
        It consists of a 3D scene rendered with OpenGL using some advanced rendering techniques, such as HDR rendering, Shadow mapping, and vertex displacement.
    }\newpage
    \cventry
    {Personal} % Empty position
    {\href{https://github.com/CRefice/oxide}{Oxide\hspace{0.15cm}\faGithubSquare}} % Project
    {} % Empty location
    {} % Empty date
    {
        An interpreted, stack-based programming language written in Rust.\newline
        The language currently supports most imperative control structures, along as extra functional features such as first-class functions.
    }\\\vspace{1em}
    \cventry
    {Personal} % Empty position
    {\href{https://github.com/CRefice/prayer}{Prayer\hspace{0.15cm}\faGithubSquare}} % Project
    {} % Empty location
    {} % Empty date
    {
        A multi-threaded stochastic path tracer with advanced features such as KD-Tree based geometry acceleration, Cook-Torrance BRDF, and importance sampling. Written in Rust.
    }
    %\cventry
    %{Personal} % Empty position
    %{\href{https://github.com/CRefice/ssm}{SSM - Speedy Simd Library\hspace{0.15cm}\faGithubSquare}} % Project
    %{} % Empty location
    %{} % Empty date
    %{
    %    A C++ Linear Algebra library making use of SIMD intrinsics for high-performance computations. It includes types and functions for vectors, matrices and quaternions.
    %    Importantly, it's fully template-based, supporting vectors of any type and dimension.
    %}
\end{cventries}
